\texttt{nevh}: Numerical Evolution from the Hamiltonian

### 2019-08-12 doc/nevh.tex
Resuming work. Cleaned up a bit.

\section{Hamilton's Equations}
The physical state of a system with $N_f$ degreees of freedom is completely
specified given the values of $2N_f$ variables $q_i$ (coordinates) and $p_i$
(momentums) $i=1,\ldots,N_f$.  Its time evolution is determined by the
Hamilton's Equations,
\begin{align}
  \dot q_i&=\pd{H}{p_i}&
  \dot p_i&=-\pd{H}{q_i},
\end{align}
where $H=H(t,q,p)$ is the hamiltonian of the system which, in many situations,
is simply the toal mechanical energy of the system, $H=T+U$. Once the partial
derivatives in the rhs of Hamilton's equations are known, they define a system
of $2N_f$ first order simultaneous ordinary differential equations (ODE) in time
for the $q$'s and the $p$'s. The solution of this system is the trajectory (in
phase space) followed by the system in its evolution.

@@

\section{Hamilton's Equations in Numerical Form}
Hamilton's
Equations can be set in a more compact (and more suitable for numerical resolution
using standard routines or in the current approach) form,
\begin{equation}\label{eq:HEterse}
  \dot \psi=f(t,\psi),
\end{equation}
where $\psi=(\psi_1,\,\psi_2,\,\ldots,\,\psi_{2N_f})=(q_i,\,p_i)$,
$i=1,\ldots N_f$ and
\begin{equation}
  f(t,\psi)=
  \begin{pmatrix}
    \mathbb{0}&\mathbb{1}\\
    -\mathbb{1} &\mathbb{O}
  \end{pmatrix}\nabla_\psi H(t,\psi).
\end{equation}
Here, $\mathbb{0}$ and $\mathbb{1}$ represent the $N_f\times N_f$ zero matrix
and identity matrix, respectively, and
\begin{equation*}
  \nabla_\psi H=\left(
    \pd{H}{\psi_1},\,
    \pd{H}{\psi_2},\,\ldots,\,
    \pd{H}{\psi_{2N_f}}
    \right).
\end{equation*}
\end{document}

>>>>

\section{Hamilton's Equations}
The physical state of a system with $N_f$ degreees of freedom is completely
specified given the values of $2N_f$ variables $q_i$ (coordinates) and $p_i$
(momentums) $i=1,\ldots,N_f$.  Its time evolution is determined by the
Hamilton's Equations,
\begin{align}
  \dot q_i&=\pd{H}{p_i}&
  \dot p_i&=-\pd{H}{q_i},
\end{align}
where $H=H(t,q,p)$ is the hamiltonian of the system which, in many situations,
is simply the total mechanical energy of the system, $H=T+U$. Once the partial
derivatives in the rhs of Hamilton's equations are known, they define a system
of $2N_f$ first order simultaneous ordinary differential equations (ODE) in time
for the $q$'s and the $p$'s. The solution of this system is the trajectory (in
phase space) followed by the system in its evolution.

@@

\section{Hamilton's Equations in Numerical Form}
Hamilton's Equations can be set in a more compact (and more suitable for
numerical resolution using standard routines or in the current approach) form,
\begin{equation}\label{eq:HEterse}
  \dot \psi=f(t,\psi),
\end{equation}
where $\psi=(\psi_1,\,\psi_2,\,\ldots,\,\psi_{2N_f})=(q_i,\,p_i)$,
$i=1,\ldots N_f$ and
\begin{equation}
  f(t,\psi)=
  \begin{pmatrix}
    \mathbb{0}&\mathbb{1}\\
    -\mathbb{1} &\mathbb{O}
  \end{pmatrix}\nabla_\psi H(t,\psi).
\end{equation}
Here, $\mathbb{0}$ and $\mathbb{1}$ represent the $N_f\times N_f$ zero matrix
and identity matrix, respectively, and
\begin{equation*}
  \nabla_\psi H=\left(
    \pd{H}{\psi_1},\,
    \pd{H}{\psi_2},\,\ldots,\,
    \pd{H}{\psi_{2N_f}}
    \right).
\end{equation*}
This package
\end{document}
